Phase paper outline your mom last night

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
new title
add notes on BP-HR phase lag

\documentclass{article}
\title{Phase paper outline}
\author{}
\date{}
\begin{document}
\maketitle

@@

\section*{Introduction}
\begin{itemize}
\item Physiological regulatory systems are reliably non-linear in their responses
\item Signal transduction, be it physical signals like pressure or cellular signals like phosphorylation, introduces a delay between input and output. 
\item Non-linearities and delays conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
\item Oscillating physiological systems can become synchronized if they are somehow physically coupled. For example, sinus arrhythmia caused by respiration. 
\item Phase information extracted from each oscillating system can provide information about the relationship between the two systems.
\item Phase is essentially how far along a cycle a particular oscillation is. 
\item The problem is that phase has been extracted by multiple different methods, and it is unclear whether there is a best option, or if specific methods are ideal for specific purposes.
\item Noise and time-variance present in physiological data makes this process more difficult.
\item The goal of this paper is to identify the most accurate methods of extracting phase information and determine how to deal with common hurdles present in physiological data.
\end{itemize}

@@

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item BP and Heart rate
	\begin{itemize}
	\item phase lag between changes in heart rate and changes in BP
	\end{itemize}
\item Something about SCG or ECG
\item cerebral blood flow
\item JESS
\end{itemize}

@@

	\subsection*{Figures}
	\begin{enumerate}
	\item Simulation
		\begin{enumerate}
		\item Time series of raw simulated data + added noise
		\item Power spectrum of the data
		\item Time-domain phase 
		\item Accuracy of each detector at a range of signal to noise ratios
		\end{enumerate}
	\item Rat data
		\begin{enumerate}
		\item BP and cortical perfusion
		\item Phase interactions between two or three regions on the renal surface
		\end{enumerate}
	\item{Human data}
		\begin{enumerate}
		\item BP and heart rate
		\item Use phase to find the lag between a change in bp and a change in heart rate
		\end{}
	\end{enumerate}

>>>>

\documentclass{article}
\title{Phase paper outline your mom last night}
\author{}
\date{}
\begin{document}
\maketitle

@@

\section*{Introduction}
\begin{itemize}
\item Physiological regulatory systems are reliably non-linear in their responses
\item Signal transduction, be it physical signals like pressure or cellular signals like phosphorylation, introduces a delay between input and output. 
\item Non-linearities and delays conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
\item Oscillating physiological systems can become synchronized if they are somehow physically coupled. For example, sinus arrhythmia caused by respiration. 
\item Phase information extracted from each oscillating system can provide information about the relationship between the two systems.
\item Phase is essentially how far along a cycle a particular oscillation is. 
\item The problem is that phase has been extracted by multiple different methods, and it is unclear whether there is a best option, or if specific methods are ideal for specific purposes.
\item Noise and time-variance present in physiological data makes this process more difficult.

\item In addition to finding the individual phase of an oscillating signal, determination of phase shift, or lag-time, between two related signals is an important physiological parameter that may offer insight into pathophysiological conditions.  
\item The goal of this paper is to identify the most accurate methods of extracting phase information and determine how to deal with common hurdles present in physiological data.
\end{itemize}

@@

\subsection*{Physiological data}
\begin{itemize}
\item Renal cortical perfusion
	\begin{itemize}
	\item phase synchronization among regions of the kidney
	\end{itemize}
\item Blood pressure and heart rate
	\begin{itemize}
	\item [Phase lag between changes in blood pressure and changes in heart rate] \hfill \\
	The oscillations of blood pressure and heart rate are often compared using cross-spectral analyses to quantify baroreflex function.  With this method, the coherence, transfer function gain, and phase relationship between the two signals are quantified.  The phase shift between blood pressure and heart rate is lengthened in some pathophysiological conditions (Javorka et al, 2011) and more variable/unstable in other conditions (Halamek et al, 2003 Circulation).  Therefore, the phase relationship between these two signals might be an important outcome measure for cardiovascular testing.  
	\end{itemize}
\item Something about SCG or ECG ?
\item Cerebral blood flow ?
\end{itemize}

@@

	\subsection*{Figures}
	\begin{enumerate}
	\item Simulation
		\begin{enumerate}
		\item Time series of raw simulated data + added noise
		\item Power spectrum of the data
		\item Time-domain phase 
		\item Accuracy of each detector at a range of signal to noise ratios
		\end{enumerate}
	\item Rat data
		\begin{enumerate}
		\item BP and cortical perfusion
		\item Phase interactions between two or three regions on the renal surface
		\end{enumerate}
	\item{Human data}
		\begin{enumerate}
		\item BP and heart rate
		\item Use phase to find the lag between a change in bp and a change in heart rate
		\end{enumerate}
	\end{enumerate}
